Towards In-Switch Reinforcement Learning

### 2020-12-02 interim-talk/talk.tex
Finalise talk.

\documentclass[aspectratio=169,xcolor={dvipsnames}
%,notes=only
%,notes
%,show notes on second screen=right
%,handout
]{beamer}
\usetheme[background=light, numbering=fraction]{metropolis}
\usepackage{appendixnumberbeamer}
\usepackage{pgfpages}

@@

\begin{frame}{How could this (hypothetically) fit the case study?}
	\begin{itemize}
		\item P4 action to gather state on collected flows.
		\begin{itemize}
			\item Flow telemetry in P4 well-documented.
			\item Pass in/schedule state vectors every $\delta{}t$.
		\end{itemize}
		\item Directly pass reward measurements to RL core.
		\item Base policy installed by controller, updated live.
		\item Matched packets poll actions from RL core.
		\begin{itemize}
			\item Map RL actions to state machine, maintain throttling hash table.
			\item Every $\delta{}t'$, batch actions to controller.
		\end{itemize}
	\end{itemize}
\end{frame}

@@

\begin{frame}{Execution costs (Q15.16)}
	\begin{columns}
		\begin{column}{0.4\linewidth}
			\begin{itemize}
				\item Single-threaded---still to be accelerated.
				\item Small? One tiling per memory tier.
				\item Versus use-case: \SI{330}{\micro\second} on commodity i7.
			\end{itemize}
		\end{column}
		\begin{column}{0.6\linewidth}
			\centering
			\begin{tabular}{ l c c }
				\toprule
				Policy Size & Action (\si{\micro\second}) & Plus Update (\si{\micro\second}) \\ \midrule
				Small & \num{10.66} & \num{14.60} \\
				Max (DDoS) & \num{512.67} & \num{612.55} \\ \bottomrule
			\end{tabular}
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}[standout]
	\begin{itemize}
		\item Online in-NIC RL is possible!
		\item In-switch? Less so.
		\item Arch-specific, but similar design for similar hardware class.
		\item Work-in-progress: end-to-end timing, training accuracy, other use-cases, optimisation.
	\end{itemize}
	\alert{Questions?}
\end{frame}

>>>>

\documentclass[aspectratio=169,xcolor={dvipsnames}
%,notes=only
%,notes
%,show notes on second screen=right
,handout
]{beamer}
\usetheme[background=light, numbering=fraction]{metropolis}
\usepackage{appendixnumberbeamer}
\usepackage{pgfpages}

@@

\begin{frame}{How could this (hypothetically) fit the case study?}
	\begin{itemize}
		\item P4 table-action to gather state on collected flows.
		\begin{itemize}
			\item Flow telemetry in P4 well-documented.
			\item Pass in/schedule state vectors every $\delta{}t$.
		\end{itemize}
		\item Directly pass reward measurements to RL core.
		\item Base policy installed by controller, updated live.
		\item Matched packets poll actions from RL core.
		\begin{itemize}
			\item Map RL actions to state machine, maintain throttling hash table.
			\item Every $\delta{}t'$, batch actions to controller.
		\end{itemize}
	\end{itemize}
\end{frame}

@@

\begin{frame}{Execution costs (Q15.16)}
	\begin{columns}
		\begin{column}{0.4\linewidth}
			\begin{itemize}
				\item Single-threaded---still to be accelerated.
				\item Small? One tiling per memory tier.
				\item Max? 20-element state, 17 mixed-dim tilings, 8 per set.
				\item Versus use-case: \SI{330}{\micro\second} on commodity i7 (\SI{4.2}{\giga\hertz}).
			\end{itemize}
		\end{column}
		\begin{column}{0.6\linewidth}
			\centering
			\begin{tabular}{ l c c }
				\toprule
				Policy Size & Action (\si{\micro\second}) & Plus Update (\si{\micro\second}) \\ \midrule
				Small & \num{10.66} & \num{14.60} \\
				Max (DDoS) & \num{512.67} & \num{612.55} \\ \bottomrule
			\end{tabular}
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}[standout]
	Takeaways:
	\begin{itemize}
		\item \alert{Online in-NIC RL is possible!}
		\item In-switch? Less so.
		\item Platform-specific, but similar design for SmartNIC hardware class.
		\item \alert{Work-in-progress}: end-to-end timing, training accuracy, other use-cases (AQM?), optimisation.
	\end{itemize}
	\alert{Questions?}
\end{frame}
